\documentclass[11pt,a4paper,sans]{letter}
\usepackage[cm]{fullpage}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{color}
\usepackage[pdftex]{hyperref}

\definecolor{resBlue}{RGB}{200,226,254}
\definecolor{linkblue}{RGB}{60,73,143}
\urlstyle{same}
\hypersetup{
	colorlinks,%
	citecolor=black,%
	filecolor=black,%
	linkcolor=linkblue,%
	urlcolor=linkblue 
}

\signature{\vspace{-40pt} Christopher Salahub}
\address{Hallwylstrasse 30 \\ 8004 Z\"urich}
\begin{document}
	\begin{letter}{Julie Tantsef and Ian Williams \\ Toronto Police Services \\ 40 College Street \\ Toronto, Ontario}

		\opening{Dear Ms. Tantsef and Mr. Williams,}
		
		My name is Christopher Salahub. I am a Canadian student pursuing my M.Sc. in statistics at ETH Zurich, and I recently came across Toronto Police Service's open Data Scientist position. Reading through the posting and researching your organization, I am convinced that I would be an excellent fit for this position upon my graduation in February of 2019. Please find my resume attached.
		
		\begin{comment}Starmind aims to remove the "e-mail lottery" expertise method from large organizations, so I would like to begin by emphasizing my experience working with text data. For my publication, \href{https://rss.onlinelibrary.wiley.com/doi/full/10.1111/j.1740-9713.2018.01148.x}{\textit{About ``her emails''}}, I used regular expressions and other tools to extract, parse, filter, and analyse a corpus of almost 33,000 emails, before finally displaying these in an \href{https://shiny.math.uwaterloo.ca/sas/clinton/}{interactive web application}. This entire project was executed in R, and has made me adept at identifying and explaining errors and inconsistencies in real-world text data, experience which I believe would be a great asset to your company.
		\end{comment}
		
		I would like to emphasize my experience working in teams on a broad range of heavily applied projects. From evaluating road risk in Zurich to modelling biological systems, I have gained experience in the application of diverse statistical methods to a wide variety of contexts, and I have consequently developed strong proficiency in both the R and Python programming languages. \begin{comment}In particular, note my experience working alongside doctors in the analysis of healthcare data as part of my statistical consulting course at ETH Z\"urich. This project gave me experience handling medical data, with all of the extra privacy considerations that entails, and also developed my sensitivity and consideration of the ultimate beneficiaries of the analysis: patients. \end{comment}
		Throughout these varied exploits, I have also gained exposure to distributed programming architectures, with project-motivated experience in parallel processing and exposure to Hadoop and Spark through a fourth-year course at the University of Waterloo. This course also introduced me to Unix systems, which I now use on my own personal computer.
		
		Additionally, allow me to bring to your attention to the breadth of statistical and mathematical study I have encountered in my undergraduate and graduate studies. During my studies at ETH Zurich and the University of Waterloo, I have taken courses which have addressed nearly all major modern machine learning techniques, and have experience implementing and interpreting a wide variety of classification, prediction, and visualization models. These include regression, support vector machines, numerous clustering methods, principal component analysis, Fisher discriminant analysis, Bayes classifiers, decision trees, local linear embedding, and many more. Many of these courses have had a heavily applied component, which has given me extensive experience in both the R and Python programming languages.
		
		Despite this serious and applied study, I have always found the most critical component to any project is effective communication. To that end, I have cultivated personal success in debate and public speaking, as demonstrated by my multiple participations in the Canadian national debate tournament. Conveying information in a clear, effective manner has always been a passion of mine, one which extends to a preoccupation with the quality and efficacy of statistical visualizations. I was the recipient of the Cherry Statistics award multiple times for achieving the highest grade in data visualization at the University of Waterloo alongside a number of other applied final year statistical courses.
		
		These multidisciplinary applications of my knowledge have frequently occurred simultaneously. My work on email analysis was carried out at the same time as my duties at Environics Analytics, a marketing firm in which I worked alongside Ph.D. researchers to develop multiple demographic models, simulations, and projections over two summers. I have consequently demonstrated my dedication to key tasks and the flexibility to work on multiple projects concurrently, especially projects which involve messy and incomplete data.
		
		Beyond my flexibility and experience, I have a strong desire to make a positive impact on the world. Meaningful work helping to save lives and help those in need motivates me, and as a result I know that at Toronto Police Services I would be diligent, committed, and compassionate in all of my work.
		
		%In short, my breadth of experience and demonstrated flexibility make me an excellent candidate for employment at Hamilton Health Services. I have demonstrated experience and excellence from conception to implementation to communication in all the large projects to which I have contributed, and would continue that strong pattern of reliability if employed.
		
		
		\closing{Sincerely,}
	\end{letter}
\end{document}